\documentclass[a4paper, 12pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{apacite}
\usepackage{mathptmx}
\usepackage{enumerate}
\usepackage[margin=0.5in]{geometry}
\usepackage{xspace}

\renewcommand{\baselinestretch}{1.0}

\newcommand\nd{\textsuperscript{nd}\xspace}
\newcommand\rd{\textsuperscript{rd}\xspace}
\newcommand\nth{\textsuperscript{th}\xspace} %\th is taken already

\setlength\parindent{0pt} % set paragraph indent to zero

% fill up your name, ID, contribution and paper title here
\author{
Student Name1 \quad Student ID1 \quad contribution1 \\
Student Name2 \quad Student ID2 \quad contribution2\\
Student Name3 \quad Student ID3 \quad contribution3\\
Student Name4 \quad Student ID4 \quad contribution4\\
}
\title{ A new method for detecting DDoS attacks with machine learning techniques }

\begin{document}
\maketitle

\section*{Executive Summary}
This includes the problem statement, objectives, research methodology, expected output and significance of output in a summary form. 
\hfill
\\
\textbf{Keywords:} keyword1, keyword2 \\

\section{Introduction}
This section contains a brief introduction on the research topic and background. \\
Citation example: \cite{Termenchy15} and \cite{Jones19}.

\section{Problem Statement}
This section discusses the problem statement.. 

\section{Research Questions, Hypotheses and Objectives}
Minimum of two and maximum of four for each of the research questions, hypotheses, and research objectives. You can use numbering/bullet point to list them out.

\section{Literature Review}
This section contains analytic discussion of the related research papers. 

\section{Research Methodology}
This section contains a description about the steps involved in research methodology, which also includes the metrics to be used for evaluating the proposed method along with the brief description of the techniques/models/methods/algorithms to be used.

You can use table/figure/image/graph in the report. All figures must have titles.

\section{Research Activities and Milestones}
Use a flowchart for the research activities and a Gantt chart for the research schedules. 

\section{Expected Results and Impact}
In this section, discussion will be on novel theories/findings/knowledge and the impact on society, nation and/or economy.


%References
\bibliographystyle{apacite}
\bibliography{MyBib}{}


\end{document}

